\Large Feature and order manipulations in a free recall task affect memory for current and future lists

### 2023-11-21 paper/main.tex

\paragraph{Defining feature-based distances.} Sorting words according to a
given relevant feature requires first defining a distance function for
quantifying the dissimilarity between the values of that feature for each pair
of words. This function varied according to the type of feature under
consideration. Semantic features (category and size) are \textit{categorical}.
For these features, we defined a binary distance function: two words were
considered to ``match'' (i.e., have a distance of 0) if their labels were the
same (i.e., both from the same semantic category or both of the same size). If
two words' labels were different for a given feature, we defined the words to
have a distance of 1. Lexicographic features (length and first letter) are
\textit{discrete}. For these features, we defined a discrete distance function.
Specifically, we defined the distance between two words as either the absolute
difference between their lengths, or the absolute distance between their
starting letters in the English alphabet, respectively. For example, two words
that started with the same letter would have a ``first letter'' distance of 0,
and a pair of words starting with `J' and `A' would have a first letter
distance of 9. Because words' lengths and letters' positions in the alphabet
are always integers, these discrete distances always take on integer values.
Finally, the visual features (color and location) are \textit{continuous} and
\textit{multivariate}, in that each ``feature'' is defined by multiple
(positive) real values. We defined the ``color'' and ``location'' distances
between two words as the Euclidean distances between their $(r, g, b)$ color
vectors and $(x, y)$ location vectors (specified as percentages of screen width
and height), respectively. Therefore, the color and location distance measures
always take on non-negative real values (upper-bounded at 439.94 for color, or
124.52 for location, reflecting the distances between the corresponding
maximally different vectors).

@@

We developed a permutation-based procedure to factor out the effects of
temporal clustering from the clustering scores for each feature dimension. For
a given set of recalled items (whose presentation positions are given by $x_1,
x_2, x_3, …, x_N$), we circularly shifted the presentation positions by a
randomly chosen amount (between 1 and the list length) to obtain a new set of
items at the (now altered) positions of the original recalls. Since the new set
of items will have the same (average) temporal distances between successive
recalls, the temporal clustering score for the new set of items will be equal
(on average) to the temporal clustering score for the original recalls.
However, we can then re-compute the feature clustering score for those new
items. Finally, we can compute a ``temporally corrected'' feature clustering
score by computing the average percentile rank of the observed (raw) feature
clustering score within the distributions of circularly shifted feature
clustering scores, across $N = 500$ repetitions of this procedure. This new
temporally corrected score provides an estimate of the observed degree of
feature clustering over and above what could be accounted for by temporal
clustering alone.

@@

\caption{\textbf{Comparing memory in the feature-rich versus reduced conditions
(all lists).} The $t$-tests reported in the table were carried out
across-participants, and reflect data aggregated across all lists from each
participant. Abbreviations used in this table are defined in
Table~\abbreviations.}

@@

\caption{\textbf{Comparing memory for early versus late lists in the
feature-rich condition.} The $t$-tests reported in the table were carried out
across-participants. Abbreviations used in this table are defined in
Table~\abbreviations.}

@@

\caption{\textbf{Comparing memory for early versus late lists in the
reduced condition.} The $t$-tests reported in the table were carried out
across-participants. Abbreviations used in this table are defined in
Table~\abbreviations.}

@@

\caption{\textbf{Comparing memory for early versus late lists in the
reduced (early) condition.} The $t$-tests reported in the table were carried out
across-participants. Abbreviations used in this table are defined in
Table~\abbreviations.}

@@

\caption{\textbf{Comparing memory for early versus late lists in the
reduced (late) condition.} The $t$-tests reported in the table were carried out
across-participants. Abbreviations used in this table are defined in
Table~\abbreviations.}

@@

\caption{\textbf{Comparing memory in the feature-rich versus reduced (early)
conditions (all lists).} The $t$-tests reported in the table were carried out
across-participants, and reflect data aggregated across all lists from each
participant. Abbreviations used in this table are defined in
Table~\abbreviations.}

@@

\caption{\textbf{Comparing memory in the reduced versus reduced (early)
conditions (all lists).} The $t$-tests reported in the table were carried out
across-participants, and reflect data aggregated across all lists from each
participant. Abbreviations used in this table are defined in
Table~\abbreviations.}

@@

\caption{\textbf{Comparing memory in the feature-rich versus reduced (late)
conditions (all lists).} The $t$-tests reported in the table were carried out
across-participants, and reflect data aggregated across all lists from each
participant. Abbreviations used in this table are defined in
Table~\abbreviations.}

@@

\caption{\textbf{Comparing memory in the reduced versus reduced (late)
conditions (all lists).} The $t$-tests reported in the table were carried out
across-participants, and reflect data aggregated across all lists from each
participant. Abbreviations used in this table are defined in
Table~\abbreviations.}

@@

\caption{\textbf{Comparing accuracy on early lists in the order manipulation
versus feature-rich conditions.} The $t$-tests reported in the table were
carried out across-participants, and reflect data aggregated across all early lists
from each participant. Abbreviations used in this table are defined in
Table~\abbreviations.}

@@

\caption{\textbf{Comparing temporal clustering on early lists in the order manipulation
versus feature-rich conditions.} The $t$-tests reported in the table were
carried out across-participants, and reflect data aggregated across all early lists
from each participant. Abbreviations used in this table are defined in
Table~\abbreviations.}

@@

\caption{\textbf{Comparing feature-based clustering on early lists in the semantic order manipulation
versus feature-rich conditions.} The $t$-tests reported in the table were
carried out across-participants, and reflect data aggregated across all early lists
from each participant. Abbreviations used in this table are defined in
Table~\abbreviations.}

@@

\caption{\textbf{Comparing feature-based clustering on early lists in the lexicographic order manipulation
versus feature-rich conditions.} The $t$-tests reported in the table were
carried out across-participants, and reflect data aggregated across all early lists
from each participant. Abbreviations used in this table are defined in
Table~\abbreviations.}

@@

\caption{\textbf{Comparing feature-based clustering on early lists in the visual order manipulation
versus feature-rich conditions.} The $t$-tests reported in the table were
carried out across-participants, and reflect data aggregated across all early lists
from each participant. Abbreviations used in this table are defined in
Table~\abbreviations.}

@@

\caption{\textbf{Comparing accuracy on early lists in different order manipulation
conditions.} The $t$-tests reported in the table were
carried out across-participants, and reflect data aggregated across all early lists
from each participant. Abbreviations used in this table are defined in
Table~\abbreviations.}

@@

\caption{\textbf{Comparing temporal clustering on early lists in different order manipulation
conditions.} The $t$-tests reported in the table were
carried out across-participants, and reflect data aggregated across all early lists
from each participant. Abbreviations used in this table are defined in
Table~\abbreviations.}

@@

\caption{\textbf{Comparing feature-based clustering on early lists in different order manipulation
conditions.} The $t$-tests reported in the table were
carried out across-participants, and reflect data aggregated across all early lists
from each participant. The feature used to compute clustering is shown before the colon in each row, and the
conditions being compared are shown after the colon.  Abbreviations used in this table are defined in
Table~\abbreviations.}

@@

\caption{\textbf{Comparing accuracy on late lists in order-manipulation
versus feature-rich conditions.} The $t$-tests reported in the table were
carried out across-participants, and reflect data aggregated across all late
lists from each participant. Abbreviations used in this table are defined in
Table~\abbreviations.}

@@

\caption{\textbf{Comparing temporal clustering on late lists in order-manipulation
versus feature-rich conditions.} The $t$-tests reported in the table were
carried out across-participants, and reflect data aggregated across all late
lists from each participant. Abbreviations used in this table are defined in
Table~\abbreviations.}

@@

\caption{\textbf{Comparing feature-based clustering on late lists in semantic order-manipulation
versus feature-rich conditions.} The $t$-tests reported in the table were
carried out across-participants, and reflect data aggregated across all late
lists from each participant. Abbreviations used in this table are defined in
Table~\abbreviations.}

@@

\caption{\textbf{Comparing feature-based clustering on late lists in
lexicographic order-manipulation versus feature-rich conditions.} The
$t$-tests reported in the table were carried out across-participants, and
reflect data aggregated across all late lists from each participant.
Abbreviations used in this table are defined in Table~\abbreviations.}

@@

\caption{\textbf{Comparing feature-based clustering on late lists in visual order-manipulation
versus feature-rich conditions.} The $t$-tests reported in the table were
carried out across-participants, and reflect data aggregated across all late
lists from each participant. Abbreviations used in this table are defined in
Table~\abbreviations.}

@@

feature clustering on early lists showed stronger temporal
clustering on later lists (overall: $r(179) = 0.464,~p < 0.001,~\mathrm{CI} =
[0.321, 0.582]$; for individual conditions: all $r$s $\geq 0.377$, all $p$s
$\leq 0.040$; across conditions: $ r(4) = 0.451,~p = 0.369,~\mathrm{CI} =
[-0.986, 0.998]$). And participants who showed stronger temporal clustering on
early lists trended towards showing stronger feature clustering on later lists
(overall: $r(179) = 0.266,~p < 0.001,~\mathrm{CI} = [0.129, 0.396]$; for
individual conditions: all $r$s $\geq 0.298$, all $p$s $\leq 0.110$; across
conditions: $r(4) = 0.064,~p = 0.903,~\mathrm{CI} = [-0.972,~0.965$). Taken together,
the results displayed in Figure~\ref{fig:clustering-scatterplots} show that
participants who were more sensitive to the order manipulations (i.e.,
participants who showed stronger feature clustering for their condition's
feature on early lists) remembered more words and showed stronger temporal
clustering. These associations also appeared to carry over across lists, even
when the items on later lists were presented in a random order.

@@

If participants show different sensitivities to order manipulations, how do
their behaviors carry over to later lists? We found that participants who
showed strong feature clustering on early lists often tended to show strong
feature clustering on late lists (Fig.~\ref{fig:clustering-carryover}A; overall
across participants and conditions: $r(179) = 0.591,~p < 0.001,~\mathrm{CI} =
[0.472,~0.682]$; category: $r(28) = 0.590,~p < 0.001,~\mathrm{CI} = [0.354,~
0.756]$; size: $r(28) = 0.488,~p = 0.006,~\mathrm{CI} = [0.134,~0.732]$;
length: $r(28) = 0.384,~p = 0.036,~\mathrm{CI} = [0.040,~0.681]$; first letter:
$r(28) = 0.202,~p = 0.284,~\mathrm{CI} = [-0.273,~0.620]$; color: $r(29) =
-0.183,~p = 0.325,~\mathrm{CI} = [-0.562,~0.258]$; location: $r(28) = 0.031, p
= 0.870,~\mathrm{CI} = [-0.240,~0.296]$; across conditions: $r(4) = 0.942,~p =
0.005,~\mathrm{CI} = [0.442,~1.000]$). Although participants tended to show
weaker feature clustering on late lists
(Figs.~\ref{fig:fingerprints},~\ref{fig:barplots}) on \textit{average}, the
associations between early and late lists for individual participants suggests
that some influence of early order manipulations may linger on late lists. We
found that participants who exhibited larger carryover in feature clustering
(i.e., continued to show strong feature clustering on late lists) for the
semantic order manipulations (but not other manipulations) also tended to show
a smaller decrease in recall on early versus late lists
(Fig.~\ref{fig:clustering-carryover}B; overall: $r(179) = 0.307,~p < 0.001,
\mathrm{CI} = [0.148,~0.469]$; category: $r(28) = 0.350,~p = 0.058,~\mathrm{CI}
= [0.050,~0.642]$; size: $r(28) = 0.708,~p < 0.001,~\mathrm{CI} = [0.472,~
0.862]$; length: $r(28) = 0.205,~p = 0.276,~\mathrm{CI} = [-0.109,~0.492]$;
first letter: $r(28) = 0.081,~p = 0.672,~\mathrm{CI} = [-0.433,~0.597]$; color:
$r(29) = 0.155,~p = 0.406,~\mathrm{CI} = [-0.174,~0.541]$; location: $r(28) =
0.052,~p = 0.787,~\mathrm{CI} = [-0.307,~0.360]$; across conditions: $r(4) =
0.635,~p = 0.176,~\mathrm{CI} = [-0.924,~0.981]$. Participants who exhibited
larger carryover in feature clustering also tended to show stronger temporal
clustering on late lists (relative to early lists) for all but the category
condition (Fig.~\ref{fig:clustering-carryover}C; overall: $r(179) = 0.426,~p <
0.001,~\mathrm{CI} = [0.285,~0.544]$; category: $r(28) = 0.110,~p = 0.564,~
\mathrm{CI} = [-0.284,~0.442]$; all non-category conditions: all $r$s $\geq
0.406$, all $p$s $\leq 0.023$; across conditions: $r(4) = 0.649,~p = 0.163,
\mathrm{CI} = [-0.856, 0.988]$).

>>>>

\paragraph{Defining feature-based distances.} Sorting words according to a
given relevant feature requires first defining a distance function for
quantifying the dissimilarity between the values of that feature for each pair
of words. This function varied according to the type of feature under
consideration. Semantic features (category and size) are \textit{categorical}.
For these features, we defined a binary distance function: two words were
considered to ``match'' (i.e., have a distance of 0) if their labels were the
same (i.e., both from the same semantic category or both of the same size). If
two words' labels were different for a given feature, we defined the words to
have a distance of 1. Lexicographic features (length and first letter) are
\textit{discrete}. For these features, we defined a discrete distance function.
Specifically, we defined the distance between two words as either the absolute
difference between their lengths, or the absolute distance between their
starting letters in the English alphabet, respectively. For example, two words
that started with the same letter would have a ``first letter'' distance of 0,
and a pair of words starting with `J' and `A' would have a first letter
distance of 9. Because words' lengths and letters' positions in the alphabet
are always integers, these discrete distances always take on integer values.
Finally, the visual features (color and location) are \textit{continuous} and
\textit{multivariate}, in that each ``feature'' is defined by multiple
(positive) real values. We defined the ``color'' and ``location'' distances
between two words as the Euclidean distances between their $(r, g, b)$ color
vectors and $(x, y)$ location vectors (specified as a percentage of the
viewable display's width), respectively. Therefore, the color and location
distance measures always take on non-negative real values (upper-bounded at
439.94 for color, or 124.52 for location, reflecting the distances between the
corresponding maximally different vectors).

@@

We developed a permutation-based procedure to factor out the effects of
temporal clustering from the clustering scores for each feature dimension. For
a given set of recalled items (whose presentation positions are given by $x_1,
x_2, x_3, …, x_L$), we circularly shifted the presentation positions by a
randomly chosen amount (between 1 and the list length, $L$) to obtain a new set of
items at the (now altered) positions of the original recalls. Since the new set
of items will have the same (average) temporal distances between successive
recalls, the temporal clustering score for the new set of items will be equal
(on average) to the temporal clustering score for the original recalls.
However, we can then re-compute the feature clustering score for those new
items. Finally, we can compute a ``temporally corrected'' feature clustering
score by computing the average percentile rank of the observed (raw) feature
clustering score within the distributions of circularly shifted feature
clustering scores, across $n = 500$ repetitions of this procedure. This new
temporally corrected score provides an estimate of the observed degree of
feature clustering over and above what could be accounted for by temporal
clustering alone.

@@

\caption{\textbf{Comparing memory in the feature-rich versus reduced conditions
(all lists).} The independent samples $t$-tests reported in the table were carried out
across-participants, and reflect data aggregated across all lists from each
participant. Abbreviations used in this table are defined in
Table~\abbreviations.}

@@

\caption{\textbf{Comparing memory for early versus late lists in the
feature-rich condition.} The paired $t$-tests reported in the table were
carried out within-participant. Abbreviations used in this table are defined in
Table~\abbreviations.}

@@

\caption{\textbf{Comparing memory for early versus late lists in the reduced
condition.} The paired $t$-tests reported in the table were carried out
within-participant. Abbreviations used in this table are defined in
Table~\abbreviations.}

@@

\caption{\textbf{Comparing memory for early versus late lists in the reduced
(early) condition.} The paired $t$-tests reported in the table were carried out
within-participant. Abbreviations used in this table are defined in
Table~\abbreviations.}

@@

\caption{\textbf{Comparing memory for early versus late lists in the reduced
(late) condition.} The paired $t$-tests reported in the table were carried out
within-participant. Abbreviations used in this table are defined in
Table~\abbreviations.}

@@

\caption{\textbf{Comparing memory in the feature-rich versus reduced (early)
conditions (all lists).} The independent samples $t$-tests reported in the
table were carried out across-participants, and reflect data aggregated across
all lists from each participant. Abbreviations used in this table are defined
in Table~\abbreviations.}

@@

\caption{\textbf{Comparing memory in the reduced versus reduced (early)
conditions (all lists).} The independent samples $t$-tests reported in the
table were carried out across-participants, and reflect data aggregated across
all lists from each participant. Abbreviations used in this table are defined
in Table~\abbreviations.}

@@

\caption{\textbf{Comparing memory in the feature-rich versus reduced (late)
conditions (all lists).} The independent samples $t$-tests reported in the
table were carried out across-participants, and reflect data aggregated across
all lists from each participant. Abbreviations used in this table are defined
in Table~\abbreviations.}

@@

\caption{\textbf{Comparing memory in the reduced versus reduced (late)
conditions (all lists).} The independent samples $t$-tests reported in the
table were carried out across-participants, and reflect data aggregated across
all lists from each participant. Abbreviations used in this table are defined
in Table~\abbreviations.}

@@

\caption{\textbf{Comparing accuracy on early lists in the order manipulation
versus feature-rich conditions.} The independent samples $t$-tests reported in
the table were carried out across-participants, and reflect data aggregated
across all early lists from each participant. Abbreviations used in this table
are defined in Table~\abbreviations.}

@@

\caption{\textbf{Comparing temporal clustering on early lists in the order
manipulation versus feature-rich conditions.} The independent samples $t$-tests
reported in the table were carried out across-participants, and reflect data
aggregated across all early lists from each participant. Abbreviations used in
this table are defined in Table~\abbreviations.}

@@

\caption{\textbf{Comparing feature-based clustering on early lists in the
semantic order manipulation versus feature-rich conditions.} The independent
samples $t$-tests reported in the table were carried out across-participants,
and reflect data aggregated across all early lists from each participant.
Abbreviations used in this table are defined in Table~\abbreviations.}

@@

\caption{\textbf{Comparing feature-based clustering on early lists in the
lexicographic order manipulation versus feature-rich conditions.} The
independent samples $t$-tests reported in the table were carried out
across-participants, and reflect data aggregated across all early lists from
each participant. Abbreviations used in this table are defined in
Table~\abbreviations.}

@@

\caption{\textbf{Comparing feature-based clustering on early lists in the
visual order manipulation versus feature-rich conditions.} The independent
samples $t$-tests reported in the table were carried out across-participants,
and reflect data aggregated across all early lists from each participant.
Abbreviations used in this table are defined in Table~\abbreviations.}

@@

\caption{\textbf{Comparing accuracy on early lists in different order
manipulation conditions.} The independent samples $t$-tests reported in the
table were carried out across-participants, and reflect data aggregated across
all early lists from each participant. Abbreviations used in this table are
defined in Table~\abbreviations.}

@@

\caption{\textbf{Comparing temporal clustering on early lists in different
order manipulation conditions.} The independent samples $t$-tests reported in
the table were carried out across-participants, and reflect data aggregated
across all early lists from each participant. Abbreviations used in this table
are defined in Table~\abbreviations.}

@@

\caption{\textbf{Comparing feature-based clustering on early lists in different
order manipulation conditions.} The independent samples $t$-tests reported in
the table were carried out across-participants, and reflect data aggregated
across all early lists from each participant. The feature used to compute
clustering is shown before the colon in each row, and the conditions being
compared are shown after the colon. Abbreviations used in this table are
defined in Table~\abbreviations.}

@@

\caption{\textbf{Comparing accuracy on late lists in order-manipulation versus
feature-rich conditions.} The independent samples $t$-tests reported in the
table were carried out across-participants, and reflect data aggregated across
all late lists from each participant. Abbreviations used in this table are
defined in Table~\abbreviations.}

@@

\caption{\textbf{Comparing temporal clustering on late lists in
order-manipulation versus feature-rich conditions.} The independent samples
$t$-tests reported in the table were carried out across-participants, and
reflect data aggregated across all late lists from each participant.
Abbreviations used in this table are defined in Table~\abbreviations.}

@@

\caption{\textbf{Comparing feature-based clustering on late lists in semantic
order-manipulation versus feature-rich conditions.} The independent samples
$t$-tests reported in the table were carried out across-participants, and
reflect data aggregated across all late lists from each participant.
Abbreviations used in this table are defined in Table~\abbreviations.}

@@

\caption{\textbf{Comparing feature-based clustering on late lists in
lexicographic order-manipulation versus feature-rich conditions.} The
independent samples $t$-tests reported in the table were carried out
across-participants, and reflect data aggregated across all late lists from
each participant. Abbreviations used in this table are defined in
Table~\abbreviations.}

@@

\caption{\textbf{Comparing feature-based clustering on late lists in visual
order-manipulation versus feature-rich conditions.} The independent samples
$t$-tests reported in the table were carried out across-participants, and
reflect data aggregated across all late lists from each participant.
Abbreviations used in this table are defined in Table~\abbreviations.}

@@

feature clustering on early lists showed stronger temporal clustering on later
lists (overall: $r(179) = 0.464,~p < 0.001,~\mathrm{CI} = [0.321, 0.582]$; for
individual conditions: all $r$s $\geq 0.377$, all $p$s $\leq 0.040$; across
conditions: $ r(4) = 0.451,~p = 0.369,~\mathrm{CI} = [-0.986, 0.998]$). And
participants who showed stronger temporal clustering on early lists trended
towards showing stronger feature clustering on later lists (overall: $r(179) =
0.266,~p < 0.001,~\mathrm{CI} = [0.129, 0.396]$; for individual conditions: all
$r$s $\geq 0.298$, all $p$s $\leq 0.110$; across conditions: $r(4) = 0.064,~p =
0.903,~\mathrm{CI} = [-0.972,~0.965$). Taken together, the results displayed in
Figure~\ref{fig:clustering-scatterplots} show that participants who were more
sensitive to the order manipulations (i.e., participants who showed stronger
feature clustering for their condition's feature on early lists) remembered
more words and showed stronger temporal clustering. These associations also
appeared to carry over to later lists, even when the items on those later lists
were presented in a random order.

@@

If participants show different sensitivities to order manipulations, how do
their behaviors carry over to later lists? We found that participants who
showed strong feature clustering on early lists often tended to show strong
feature clustering on late lists (Fig.~\ref{fig:clustering-carryover}A; overall
across participants and conditions: $r(179) = 0.591,~p < 0.001,~\mathrm{CI} =
[0.472,~0.682]$; category: $r(28) = 0.590,~p < 0.001,~\mathrm{CI} = [0.354,~
0.756]$; size: $r(28) = 0.488,~p = 0.006,~\mathrm{CI} = [0.134,~0.732]$;
length: $r(28) = 0.384,~p = 0.036,~\mathrm{CI} = [0.040,~0.681]$; first letter:
$r(28) = 0.202,~p = 0.284,~\mathrm{CI} = [-0.273,~0.620]$; color: $r(29) =
-0.183,~p = 0.325,~\mathrm{CI} = [-0.562,~0.258]$; location: $r(28) = 0.031, p
= 0.870,~\mathrm{CI} = [-0.240,~0.296]$; across conditions: $r(4) = 0.942,~p =
0.005,~\mathrm{CI} = [0.442,~1.000]$). Although participants tended to show
weaker feature clustering on late lists
(Figs.~\ref{fig:fingerprints},~\ref{fig:barplots}) on \textit{average}, the
associations between early and late lists for individual participants suggests
that some influence of early order manipulations may linger on late lists. We
found that participants who exhibited larger carryover in feature clustering
(i.e., continued to show strong feature clustering on late lists) for the
semantic order manipulations (but not other manipulations) also tended to show
a smaller decrease in recall on early versus late lists
(Fig.~\ref{fig:clustering-carryover}B; overall: $r(179) = 0.307,~p < 0.001,
\mathrm{CI} = [0.148,~0.469]$; category: $r(28) = 0.350,~p = 0.058,~\mathrm{CI}
= [0.050,~0.642]$; size: $r(28) = 0.708,~p < 0.001,~\mathrm{CI} = [0.472,~
0.862]$; length: $r(28) = 0.205,~p = 0.276,~\mathrm{CI} = [-0.109,~0.492]$;
first letter: $r(28) = 0.081,~p = 0.672,~\mathrm{CI} = [-0.433,~0.597]$; color:
$r(29) = 0.155,~p = 0.406,~\mathrm{CI} = [-0.174,~0.541]$; location: $r(28) =
0.052,~p = 0.787,~\mathrm{CI} = [-0.307,~0.360]$; across conditions: $r(4) =
0.635,~p = 0.176,~\mathrm{CI} = [-0.924,~0.981]$). Participants who exhibited
larger carryover in feature clustering also tended to show stronger temporal
clustering on late lists (relative to early lists) for all but the category
condition (Fig.~\ref{fig:clustering-carryover}C; overall: $r(179) = 0.426,~p <
0.001,~\mathrm{CI} = [0.285,~0.544]$; category: $r(28) = 0.110,~p = 0.564,~
\mathrm{CI} = [-0.284,~0.442]$; all non-category conditions: all $r$s $\geq
0.406$, all $p$s $\leq 0.023$; across conditions: $r(4) = 0.649,~p = 0.163,
\mathrm{CI} = [-0.856, 0.988]$).
